Exploring probability distributions for bivariate temporal granularities

### 2019-08-12 main.Rmd
changed intro of calendar categorisation

<!-- general calendar categorisation -->
Often we partition time into months, weeks, days and so on in a hierarchical manner to relate it to data. Such discrete abstractions of time can be thought of as time granularities [@aigner2011visualization]. Providing a formalism to this abstraction is important to model a time series across differently grained temporal domains. Examples of time abstractions may also include day-of-week, time-of-day, week-of-year, day-of-month, month-of-year, workingday/non-workingday, etc which are useful to represent periodicity in the data. Many of these are circular, such as day-of-week, time-of-day. Some are nearly circular such as day-of-month. Some are irregular such as workingday/non-working day. Let us call all of these different abstractions of time as "calendar categorizations".

These calendar categorisations can be linear, circular or aperiodic. We call the calendar categorisations as "linear" if they respect the linear progression of time. We call these _*linear time granularities*_. Examples include hours, days, weeks and months. _*Circular time granularities*_ accommodate periodicities in time such as hour of the day, and day of the week. _*Aperiodic circular granularities*_ are neither linear nor circular, such as day of the month or public holidays.

@@

>>>>

<!-- general calendar categorisation -->
Often we partition time into months, weeks, days and so on in a hierarchical manner to relate it to data. Such discrete abstractions of time can be thought of as time granularities [@aigner2011visualization]. Examples of time abstractions may also include day-of-week, time-of-day, week-of-year, day-of-month, month-of-year, workingday/non-workingday, etc which are useful to represent different periodicities in the data. Let us call all of these different abstractions of time as "calendar categorizations".

These calendar categorisations can be linear, circular or aperiodic. The calendar categorisations as "linear" if they respect the linear progression of time. We call these **linear time granularities**. Examples include hours, days, weeks and months. **Circular time granularities** accommodate periodicities in time such as hour of the day, and day of the week. **Aperiodic circular granularities** are neither linear nor circular, such as day of the month or public holidays.

@@

Providing a formalism to these abstractions is important to model a time series across differently grained temporal domains.
